### 2019-08-17 reports/article.tex
added another citation of Bosch et al. 2019 in context

As urbanization unfolds, urban patches are expected to grow, which suggests that eventually urban patches coalesce and thus the small ones disappear. Yet this contrasts with the continuous fragmentation of natural patches and the persistence of the power-law scaling of the urban patches observed in the present study.
As a matter of fact, the complexity sciences offer a number of high-level models that intend to explain the emergence and persistence of fractal structures and power-law distributions, such as Zipf's principle of minimal effort \citep{zipf1949human}, or the concept of self-organized criticality \citep{bak1988self}.
Nevertheless, convincingly linking the observed urban patterns to models that account for socioeconomic, cultural and political drivers of urbanization remains a challenge \citep{batty2001modelling, manson2006complexity}.

>>>>

As urbanization unfolds, urban patches are expected to grow, which suggests that eventually urban patches coalesce and thus the small ones disappear. Yet this contrasts with the continuous fragmentation of natural patches and the persistence of the power-law scaling of the urban patches observed in the present study.
As a matter of fact, the complexity sciences offer a number of high-level models that intend to explain the emergence and persistence of fractal structures and power-law distributions, such as Zipf's principle of minimal effort \citep{zipf1949human}, or the concept of self-organized criticality \citep{bak1988self}.
Nevertheless, convincingly linking the observed urban patterns to models that account for socioeconomic, cultural and political drivers of urbanization remains a challenge \citep{batty2001modelling, manson2006complexity, bosch2019addressing}.
